% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.

% Start a document with the here given default font size and paper size.
\documentclass[11pt,a4paper]{article}
% Set the page margins.
\usepackage[a4paper,margin=0.5in]{geometry}
% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}
% Makes resume-specific commands available.
\usepackage{resume}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{{Joseph M. Carmack} }{}{Last update on \today. Prepared using \LaTeX.}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \\ breaks the line into a new paragraph
\noindent\href{mailto:joseph.liping@gmail.com}{joseph.liping\mbox{}@\mbox{}gmail.com}\sbull
801.755.2771\sbull
109 Dakota Trail, Farmington, AR 72730\sbull\href{https://josephcarmack.github.io/}{personal website}

\roottitle{Profile}  % a root section title
\spacedhrule{0.2em}{0.2em}  % a horizontal line with some vertical spacing before and after

Researcher with a background in computational science and machine learning seeking 
employment opportunities where I can help develop solutions to complex technical problems.

\roottitle{Skills}

\spacedhrule{0.2em}{0.2em}  % a horizontal line with some vertical spacing before and after

  {\bodytext{
      \begin{itemize}
          \item Software Development: C++, Python, Git
          \item Machine Learning and AI: Using \& developing deep learning
              techniques in supervised, un-supervised, and reinforcement learning contexts.
          \item Software acceleration techiniques, including parallel 
              computing (MPI, CUDA).
          \item Data Analysis and Visualization: Paraview, Matlab, Python (Numpy, Scipy, Matplotlib etc.)
          \item Scripting Languages: Python, Bash
      \end{itemize}
  }}

\roottitle{Education}
\spacedhrule{0.2em}{0.2em}  % a horizontal line with some vertical spacing before and after

\headedsection
  {\href{https://www.uark.edu/}{University of Arkansas}}
  {\textsc{Fayetteville, AR}} {%
      \headedsubsection
     {PhD in Mechanical Engineering, GPA 4.0}
     {2013 -- 2018}
     {\bodytext{
         \begin{itemize}
             \item Graduate Coursework Highlights: Artificial Intelligence, Machine Learning, 
                 GPU Programming, Concurrent Computing, Numerical Methods, Entrepreneurship, 
                 Einstien's Theories of Relativity.
         \end{itemize}
     }}
}

\headedsection
  {\href{http://www.byui.edu/}{Brigham Young University-Idaho}}
  {\textsc{Rexburg, ID}} {%
      \headedsubsection
     {Bachelor of Science in Physics (Minor Mathematics), GPA 3.87}
     {2009 -- 2013}
     {\bodytext{
         \begin{itemize}
             \item Coursework Highlights: Quantum Mechanics, Scientific 
                 Computing, Software Development
             \item Sigma Pi Sigma nomination (top 5\% of my class).
         \end{itemize}
     }}
}

\roottitle{Research Experience (Chronological)}
\spacedhrule{0.2em}{0.2em}  % a horizontal line with some vertical spacing before and after

\headedsection
  {\href{http://comp.uark.edu/~pmillett/Members.html}{Millett Research Group}}
  {\textsc{Fayetteville, AR}} {%
      \headedsubsection
     {Graduate Research Assistant}
     {Aug \apo13 -- present}
     {\bodytext{
         \begin{itemize}
             \item Graduate research in mesoscale materials modeling.
             \item Design and development of Phase Field/Brownian 
                 dynamics C++ simulation and post-processing codes for 
                 heterogeneous HPC architectures.
             \item Forming and testing hypotheses using computational 
                 models probed via computer simulation.
             \item Extensive data analysis and visualization mostly done
                 using custom python and paraview scripts.
             \item Multiple publications (DOI: 10.1063/1.4932191, 10.1039/c7sm00317j),
                 copies available upon request.
             \item Presentations: Three conference talks at 
                 international conferences and one conference poster.
         \end{itemize}
     }}
}

\headedsection
  {\href{www.inl.gov}{Idaho National Lab Research Intern}}
  {\textsc{Idaho Falls, ID}} {%
      \headedsubsection
     {Research Assistant}
     {May \apo13 -- Feb \apo14}
     {\bodytext{
         \begin{itemize}
             \item Studied the properties of grain boundaries in Uranium Dioxide nuclear fuel via atomistic simulation.
             \item Gave an oral presentation describing research results at an international research conference (TMS 2014).
         \end{itemize}
     }}
}

\headedsection
  {\href{http://www.byu.edu}{Brigham Young University}}
  {\textsc{Provo, UT}} {%
      \headedsubsection
     {Physics REU}
     {May \apo12 -- Aug \apo12}
     {\bodytext{
         \begin{itemize}
             \item Research project in condensed matter crystallography. Applied group theory based symmetry analysis to identify complex magnetic crystal structures.
         \end{itemize}

     }}
}

\spacedhrule{0.2em}{0.2em}  % a horizontal line with some vertical spacing before and after

\inlineheadsection
  {Honors and Awards:}
  {Doctoral Academy Fellowship (\$10,000/yr for 4 years),  1st Place in university-wide poster competion, Eagle Scout}

\inlineheadsection
  {Interests (non-exhaustive):}
  {
      The study of intelligence (AI, the brain, consciousness), 
      Mandarin Chinese (I lived in Taiwan for 2 years), 
      teaching (full-course instructor for undergraduate numerical methods course), 
      fundamental physics, volunteer service, physical fitness, open source, 
      homesteading, piano and ukulele, classical education,...
  }

\end{document}
